%-------------------------
% Gaurav Raj - Resume Template (Optimized)
% Github: https://github.com/thehackersbrain/resume
%------------------------

\documentclass[10pt]{article}

% Package loading - grouped by function
\usepackage[margin=0.3in, a4paper]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}

% PDF metadata
\hypersetup{
  pdftitle={Gaurav Raj - Security Researcher \& Software Engineer Resume},
    pdfauthor={Gaurav Raj},
    pdfsubject={Resume},
pdfkeywords={Security Researcher, Systems Engineer, Red Team Operator, Penetration Tester, Software Engineer, Rust, C, Assembly, Linux, AWS, GCP}}

% Section formatting - consolidated
\setcounter{secnumdepth}{0}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{}[\titlerule]
\titleformat*{\subsubsection}{\normalsize\itshape}

% Adjust these values to squeeze/expand vertical space
\titlespacing{\section}{0pt}{4pt}{3pt}     
\titlespacing{\subsection}{0pt}{2pt}{0pt}   
\titlespacing{\subsubsection}{0pt}{0pt}{0pt}

% List formatting
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=2em}
\setlist[enumerate]{noitemsep, topsep=0pt, leftmargin=1.2em}
\setlist[description]{noitemsep, topsep=0pt, leftmargin=0.5em}

% Remove page numbers
\pagestyle{empty}

% Custom commands for consistency
\newcommand{\resumeSubheading}[4]{
    \subsection*{#1 \hfill #2}
    \subsubsection*{#3 \hfill #4}
    \vspace{2pt}
}

\newcommand{\projectSubheading}[4]{
    \subsection*{#1 $|$ \normalfont\textit{\href{#2}{#3}} \hfill #4}
    \vspace{3pt}
}

\begin{document}

% Header - optimized layout
\begin{center}
	\begin{minipage}{0.65\textwidth}
		{\Huge\bfseries Gaurav Raj} \\
		\\
		\textbf{Security Researcher $\cdot$ Systems Engineer $\cdot$ Open Source Architect} \newline
		Patna, Bihar, India
	\end{minipage} \hfill
	\begin{minipage}{0.30\textwidth}
		\raggedleft
		\href{tel:+917488930330}{Mobile: +917488930330} \\
		\href{mailto:gaurav@thehackersbrain.xyz}{Email: gaurav@thehackersbrain.xyz} \\
		\href{https://github.com/thehackersbrain}{GitHub: github.com/thehackersbrain} \\
		\href{https://thehackersbrain.xyz/}{Website: thehackersbrain.xyz} \\
		\href{https://www.linkedin.com/in/thehackersbrainn}{LinkedIn: @thehackersbrainn}
	\end{minipage}
\end{center}

\noindent
\begin{tabular}{@{}l c r@{}}
	\textbf{Father's Name: Surendra Kumar} \quad | \quad &
	\textbf{DOB: 04/01/2006} \quad | \quad               &
	\textbf{Address: Gopaichak, Saksohara, Patna, Bihar}
\end{tabular}

%------------------------------------------------------------------------------------
%   PROFILE
%------------------------------------------------------------------------------------
\section{Profile}
\noindent Offensive Security Researcher \& Systems Engineer with \textbf{8 years of continuous open-source contribution} (1,600+ commits in 2025). Skilled in \textbf{low-level programming (C/ASM/Rust)}, OS architecture, and \textbf{Offensive Security}. Creator of the \textbf{BerserkArch} Linux distribution. Bridging the gap between Kernel-level Engineering and Full-Stack App Development.


\section{Technical Arsenal}

\begin{description}
	\item[Core Languages] C, C++, Assembly, Rust, Golang, Python, Bash, Zig, JavaScript, TypeScript, Java.
	\item[Systems Engineering] Kernel Dev, Memory Management, Bootloaders, Device Driver Development, Embedded/IoT.
	\item[Full-Stack Dev] Frontend (React/Next.js/Astro.js), Mobile (Android/IOS), Desktop Apps, Backend, Automation, APIs.
	\item[Cloud \& DevOps] AWS (SES, EC2, S3), GCP, Terraform, Vagrant, Kubernetes, Docker, Github Actions, CI/CD, Linux.
	\item[Red Teaming \& Pentesting] Reverse Engineering, Network/Internal/Web Penetration Testing, C2 (Cobalt Strike/Sliver).
\end{description}

\section{Engineering Experience}

\resumeSubheading
{BerserkArch Linux Distro Project}{Remote}
{Lead Maintainer, Developer \& Systems Architect}{2025 - Present}
\begin{itemize}
	\item \textbf{Distro Architecture:} Designed and actively maintain an Arch Linux-based distro for Red Team Operations \& Dev.
	\item \textbf{Release Engineering:} Built a fully automated CI/CD pipeline using \textbf{GitHub Actions} and \textbf{Docker} to build ISOs, verify checksums, and deploy to multiple mirrors (SourceForge, R2, Torrent) without human intervention.
	\item \textbf{Containerization:} Maintain official Docker images on \textbf{Docker Hub}, enabling rapidly deployable security environments.
	\item \textbf{Security Hardening:} Added custom kernel patches and pre-configured AppArmor profiles to ensure security for users.
\end{itemize}

\resumeSubheading
{Cybercraft Labs Pvt Ltd}{Patna, Bihar}
{Founder \& Principal Engineer (Security Consultancy)}{Sept 2023 -- Nov 2024}
\begin{itemize}
	\item \textbf{Agency Leadership:} Founded and operated an independent security consultancy, managing client lifecycles from technical consultation to delivery of penetration testing and cloud security solutions.
	\item \textbf{Cloud Architecture:} Managed hybrid cloud infrastructure (AWS/GCP) for clients, configuring secure transactional mail servers using \textbf{AWS SES} (SPF/DKIM/DMARC) and hardening EC2 instances.
	\item \textbf{Software Development} Developed full-stack web applications, desktop tools, and custom reconnaissance automation (Python/Go), optimizing client workflows and reducing manual testing time by 40\%.
\end{itemize}

\section{Key R\&D Projects}

\projectSubheading
{THBOS (Custom x86 Kernel)}{https://github.com/thehackersbrain/cpuinfo-os}{Source Code}
{\textit{Systems Programming (C, Assembly \& Zig)}}
\begin{itemize}
	\item \textbf{Kernel Dev}: Wrote a 64-bit OS kernel from scratch, implementing a custom \textbf{bootloader} to switch from Real Mode to Protected Mode.
	\item \textbf{Hardware Interaction}: Directly manipulated \textbf{CPU} registers to use \textit{CPUID} instruction set to fetch processor topology.
\end{itemize}

\subsection*{CarePulse $|$ \normalfont\textit{\href{https://carepulse-theta.vercel.app/}{Live App}} | \textit{\href{https://github.com/thehackersbrain/carepulse}{Source Code}} \hfill \textit{Healthcare Plaatform (Next.js, TypeScript, Appwrite)}}
\vspace{3pt}
\begin{itemize}
	\item \textbf{Full-Stack Engineering}: Architected a HIPAA-compliant patient management system with complex form validation (Zod), Next.js Server Actions and SMS notifications (Twilio).
	\item \textbf{System Design}: Built a scalable backend with admin panel with Server Actions for secure data handling.
\end{itemize}

\projectSubheading
{Chip8 Emulator}{https://github.com/thehackersbrain/chip8}{github.com/thehackersbrain/chip8}
{\textit{Systems Emulation (Rust)}}
\begin{itemize}
	\item \textbf{Emulation Logic:} Built a fully functional CHIP-8 emulator in Rust, implementing the fetch-decode-execute cycle and stack management.
	\item \textbf{Memory Safety:} Leveraged Rust's borrow checker to ensure memory safety while handling raw bytecode execution.
\end{itemize}

\projectSubheading
{HiddenWave}{https://github.com/thehackersbrain/hiddenwave}{github.com/thehackersbrain/hiddenwave}
{\textit{Steganography Tool (C++ \& Python)}}
\begin{itemize}
	\item \textbf{Bit Manipulation:} Implemented Least Significant Bit (LSB) encoding algorithms in C++ to hide encrypted payloads inside WAV/MP3 audio.
\end{itemize}

\section{Achievements \& Certifications}

\begin{itemize}[leftmargin=2em]
	\item \textbf{VulnHub Author:} Architected 2 official vulnerable VMs (\href{https://www.vulnhub.com/entry/blogger-1,675/}{\textit{Blogger}}, \href{https://www.vulnhub.com/entry/corpvision-1,691/}{\textit{CorpVision}}), designing custom exploit chains involving Webmin and Cronjob privilege escalation.
	\item \textbf{Advanced Security Labs:} Completed \textbf{HackTheBox Fortresses} (Jet) \& \textbf{TryHackMe Networks} (Wreath, Holo), mastering pivoting, AD exploitation, and perimeter breaching.
	\item \textbf{Global Rankings:} \textbf{Top 1\% on TryHackMe} (CTF) $|$ \textbf{HackerRank Gold Badge} (Problem Solving \& Algorithms).
	\item \textbf{Certifications:} Certified proficiency in \textbf{Computer Forensics}, \textbf{Malware Analysis}, and \textbf{Active Directory Security} (Udemy/Independent Coursework).
\end{itemize}


\section{Education}

\begin{tabular}{@{} p{0.3\textwidth} p{0.43\textwidth} r @{}}
	\textbf{B.Sc (Maths Hons)} & \textit{Patliputra University, Patna}                       & \textbf{3rd Year, (\textit{Pursuing})} \\
	\textit{Specialization}:   & \textit{Advanced Mathmetics (ie. Calculus, Linear Algebra)} & \textbf{-}                             \\
	% \textit{Background}:               & \textit{Transferred from B.Sc (Maths Hons)}.                & \textbf{3rd Year}                      \\
\end{tabular}

\end{document}
